An Analysis of Health & Lifestyle Factors Associated with Sleep Quality

### 2024-04-21 products/manuscript/Manuscript.qmd
I figured out the references!

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-18-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../manuscript/dataanalysis-references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

*INCLUDED IN .BIB FILE* 
*IF ANYONE HAS TIPS ON HOW TO GET THE REFERENCES IN THE MANUSCRIPT ITSELF PLEASE HELP!*

>>>>

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-18-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../manuscript/references_sleepdata.bib
editor: 
  markdown: 
    wrap: 72
---

@@
